elton trait

### 2021-01-15 data-raw/elton.Rmd
Clean up data storage

```{r}
usethis::use_data(elton_bird, elton_mamm)
```

>>>>

```{r}
#save locally
usethis::use_data(elton_bird, elton_mamm)

#save to cache
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
pins::pin(elton_bird, board = "github")
pins::pin(elton_mamm, board = "github")
```
